Dirac neutrino mass generation from Majorana messenger

### 2019-08-13 draft.tex
nn

A not-so-minimal model can be obtained as the one-loop realization of
the effective 5-dimensional operator for Dirac neutrino masses~\cite{Gu:2006dc}
\begin{align}
  \label{eq:ld5}
  \mathcal{L}_{5D}=\frac{1}{\Lambda} \overline{L_i} H \nu_R S\,,
\end{align}
as displayed in fig.~\ref{fig:ld5}.
In this case we can use the standard $\operatorname{U}(1)_{B-L}$
charge of $-1$ for the lepton doublets.
It is well established that the solution for anomaly cancellation
conditions with three quiral fields with exotic
$\operatorname{U}(1)_{B-L}$ charges: $-4$,~$-4$,~$5$,  when assigned to the
three light right-handed neutrinos can forbid three level Dirac and
Majorana masses~\cite{Calle:2018ovc}.
The presence of a set of heavy Majorana mediators to realize the
dimension-5 operator at one-loop with the diagram in
fig.~\ref{fig:ld5}., would spoil the anomaly cancellation conditions.
However, we can further add an extra set of quiral fermion in a
vector-like way, such that the full set heavy fermions do not affect
the anomaly cancellation. A such assignment is displayed in
Table~\ref{tab:partcont2}.
The fields $\xi_{L \alpha}$ guarantee the anomaly cancellation and
their Majorana masses are obtained in the same way than the ones for
$\psi_{R\alpha}$.

@@

>>>>

A not-so-minimal model can be obtained as the one-loop realization of
the effective 5-dimensional operator for Dirac neutrino masses~\cite{Gu:2006dc}
\begin{align}
  \label{eq:ld5}
  \mathcal{L}_{5D}=\frac{1}{\Lambda} \overline{L_i} H \nu_R S\,,
\end{align}
as displayed in fig.~\ref{fig:ld5}.
In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Campos:2017dgc}.
We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM. The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
\begin{align}
  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
\end{align}
The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos. For $\alpha$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
\begin{align}
  \sum_{\alpha} n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha} n_{\alpha}^3+3 (e-2l)^3=&0\,. &
\end{align}

We are interested here in the case of the exotic set of $X$-charges
charges: $\mp 4$,~$\mp 4$,~$\pm 5$, that when assigned to the
three light right-handed neutrinos can forbid three level Dirac and
Majorana masses~\cite{Calle:2018ovc}. This set is compatible with the
Abelian gauge groups $X=B-L,A,B,D,G$ defined in~\cite{Campos:2017dgc}.
The presence of a set of heavy Majorana mediators to realize the
dimension-5 operator at one-loop with the diagram in
fig.~\ref{fig:ld5}., would spoil the anomaly cancellation conditions.
However, we can further add an extra set of quiral fermion in a
vector-like way, such that the full set heavy fermions do not affect
the anomaly cancellation. A such assignment is displayed in
Table~\ref{tab:partcont2}.
The fields $\xi_{L \alpha}$ guarantee the anomaly cancellation and
their Majorana masses are obtained in the same way than the ones for
$\psi_{R\alpha}$.

@@

Prospect on $N_{\text{eff}}$~\cite{Abazajian:2019oqj}
